---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dlr

<!-- badges: start -->
<!-- badges: end -->

The goal of dlr is to provide a friendly wrapper around the common pattern of downloading a file if that file does not already exist locally. 

## Installation

You can install the released version of dlr from [CRAN](https://CRAN.R-project.org) with:

``` r
# Not yet.
# install.packages("dlr")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("macmillancontentscience/dlr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(dlr)
## basic example code
```

Example coming soon.

## Code of Conduct

Please note that the dlr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## Disclaimer

This is not an officially supported Macmillan Learning product.

## Contact information

Questions or comments should be directed to Jonathan Bratt (jonathan.bratt@macmillan.com) and Jon Harmon (jonthegeek@gmail.com).
