---
title: "Integrating into Your Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Integrating into Your Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The primary purpose of this package is for use within other packages. 
To do so, you most likely want to wrap some of the exported functions from this package.

## download_cache

The primary use for {dlr} is to download data to an app cache if that data does not already exist.
Wrap `download_cache` for any files you wish to cache. 

Tip: If you will allow users to download multiple files with different URLs, define the URLs as internal data.
That way you can edit all URLs in one location without having to search through multiple functions.
For example, in the example below, `.my_url` is an internal data object with the URL of the file of interest.

```{r download_cache, eval = FALSE}
my_big_dataset <- function() {
  filepath <- dlr::download_cache(
    url = .my_url,
    appname = "myPackage"
  )
  return(readRDS(filepath))
}
```

## app_cache_dir

If you want the user to be able to easily determine the location of the cache for your package (often useful even if you don't think it will be), provide a wrapper around `app_cache_dir`

```{r app_cache_dir, eval = FALSE}
myPackage_cache_dir <- function() {
  return(dlr::app_cache_dir(appname = "myPackage"))
}
```

## set_app_cache_dir

Users will have use cases you aren't prepared for, such as a strange file system or a shared cache directory specifically for your package. Allow them to set up such options with `set_app_cache_dir`.

```{r set_app_cache_dir, eval = FALSE}
set_myPackage_cache_dir <- function(cache_dir) {
  return(dlr::set_app_cache_dir(appname = "myPackage", cache_dir = cache_dir))
}
```
